A Compound Decision Approach to Covariance Matrix Estimation

### 2021-09-20 msg.tex

Covariance matrix estimation is a fundamental statistical problem that plays an essential role in various applications, such as portfolio management \citep{ledoit2003improved}, genomics \citep{schafer2005shrinkage}, and array signal processing \citep{abramovich2001locally}. However, in modern problems the number of features can be of the same order as or exceed the sample size, and the standard sample covariance matrix estimator behaves poorly in this regime. To overcome these issues, various methods have been developed to estimate high-dimensional covariance matrix. These can roughly be divided into two groups, according to whether they impose assumptions about the structure of population covariance matrix.

Structured methods make structural assumptions about the population covariance matrix. One class models the population covariance matrix as sparse. The most common method to address this problem is thresholding \citep{rothman2009generalized, cai2011adaptive}. Penalized likelihood methods \citep{xue2012positive} can also estimate large-scale sparse covariance matrix by penalizing a log-likelihood function. Another class of methods assume the data arise from a factor model \citep{fan2008high}, so that the covariance matrix has low intrinsic dimension. Other common structured methods assume that the covariance matrix is banding \citep{li2017estimation} or Toeplitz matrix \citep{liu2017covariance}.

In contrast, unstructured methods do not make any assumptions about the population covariance matrix, yet can still outperform the sample covariance matrix. A first example was the linear shrinkage approach of \citet{ledoit2004well}, which shrinks the sample covariance matrix toward a scaled identity matrix. More recently, nonlinear shrinkage methods were developed \citep{ledoit2012nonlinear, ledoit2019quadratic, lam2016nonparametric}. These shrink the eigenvalues of the sample covariance matrix toward clusters. Linear shrinkage can be viewed as a special case of nonlinear shrinkage, as it shrinks sample eigenvalues toward their global mean.

Nonlinear shrinkage estimators have desirable optimality properties \citep{ledoit2018analytical} and show excellent performance. However, they modify only the sample eigenvalues and not the sample eigenvectors. It is known that sample eigenvectors are not consistent estimators of population eigenvectors when the dimension and the sample size increase at the same rate \citep{mestre2008asymptotic}. This suggests that there may exist a class of unstructured estimators that can outperform nonlinear shrinkage.

@@

Here we propose a new unstructured estimator for high-dimensional covariance matrices. Our approach centers on vectorizing the covariance matrix and treating matrix estimation as a vector estimation problem. We do this because it allows us to use a nonparametric empirical Bayes shrinkage procedure, which has been shown in the compound decision literature to have excellent properties \citep{jiang2009general, koenker2014convex}. We then reassemble the estimated vector into matrix form and project onto the space of positive-definite matrices to give our final estimator. Surprisingly, though our vectorized approach essentially ignores the matrix structure, it can still substantially outperform a number of state-of-the-art proposals in simulations and a real data analysis.

The article is organized as follows. In Section \ref{sec:method}, we briefly review compound decision theory and then introduce our proposed approach. In Section \ref{numerical results} we illustrate the performance of our method in simulations and a gene expression dataset. Finally, Section \ref{sec:discussion} concludes with a discussion. Our procedure is implemented in the R package \verb|cole|, available on GitHub.

@@

Our proposed approach is motivated by two observations. First, \ref{frobenius risk} shows that estimating $\bs{\Sigma}$ under Frobenius risk is equivalent to simultaneously estimating every component of the vector $(\sigma_{11},\ldots,\sigma_{pp})^\top$ under a loss function that aggregates errors across components. Second, this type of vector estimation problem has been well-studied in the compound decision literature. Thus, recent advances in vector estimation may be profitably applied to covariance matrices.

We first briefly review compound decision problems. Introduced by \citet{robbins1951asymptotically}, these problems study the simultaneous estimation of multiple parameters $\bs{\theta} = (\theta_1, \ldots, \theta_n)^\top$ given data $\bs{Y} = (Y_1, \ldots, Y_n)^\top$, with $Y_i\sim P_{\theta_i}$. Specifically, the goal is to develop a decision rule $\bs{\delta}(\bs{Y}) = (\delta_1(\bs{Y}),\ldots,\delta_n(\bs{Y}))$ that minimizes the compound risk
\begin{equation}
\label{compound risk}
R(\bs{\theta},\bs{\delta}) = \frac{1}{n}\sum_{i=1}^n \bb{E} L(\theta_i,\delta_i(\bs{Y}))
\end{equation}
where $L$ is a loss function measuring the accuracy of $\delta_i(\bs{Y})$ as an estimate of $\theta_i$. A classical example is the homoscedastic Gaussian sequence problem, where $Y_i \sim N(\theta_i, 1)$ independently and $L(t, d) = (t - d)^2$ is squared error loss \citep{johnstone2017gaussian}.

@@

We propose to apply some of these recent vector estimation ideas to covariance matrix estimation. Clearly, covariance matrix estimation under the Frobenius risk \ref{frobenius risk} can be viewed as a compound decision problem. Furthermore, some existing covariance matrix estimation procedures can already be interpreted as taking a vector approach. The sample covariance matrix $\bs{S}$, for instance, can be thought of as estimating each component of $(\sigma_{11},\ldots,\sigma_{pp})^\top$ using maximum likelihood. Less trivially, \citet{cai2011adaptive} studied sparse high-dimensional covariance matrices and explicitly appealed to the vector perspective. Their adaptive thresholding method is a version of the soft thresholding method of \citet{donoho1995adapting}, which was originally developed to estimate a sparse mean vector in the Gaussian sequence problem.

Interestingly, we can also show that the celebrated linear shrinkage covariance matrix estimator of \citet{ledoit2004well} can be interpreted as a vector estimator. The estimator is defined as
\begin{equation}
\label{linear model}
\widehat{\bs{\Sigma}}_{\text{LW}} = \widehat{\rho}_{\text{LW}} \bs{S} + (1-\widehat{\rho}_{\text{LW}})\widehat{\mu} \bs{I}
\end{equation} 
where $\widehat{\mu} = \text{tr}(\bs{S})/p$, and $\widehat{\rho}_{\text{LW}} = 1 - b_n^2 / d_n^2$ for $d_n^2=\|\bs{S}-\widehat{\mu} \bs{I} \|_F^2$ and $b_n^2 = \sum_{i=1}^n \| \bs{X}_i \bs{X}_i^\top - \bs{S} \|_F^2 / n^2$. Now consider the problem of estimating the vectorized $\bs{\Sigma}$ under risk \ref{frobenius risk}. We restrict attention to decision rules that estimate each component $\sigma_{jk}$ using
\begin{equation}
  \label{linear class}
  \beta_S s_{jk} + \beta_I u_{jk},
\end{equation}
where $s_{jk}$ is the $jk$th entry of $\bs{S}$, $u_{jk}$ is the $jk$th entry of $\bs{I}$, and the class is indexed by the parameters $(\beta_S, \beta_I)$. It is straightforward to show that
$$\widehat{R}(\beta_S,\beta_I) = \frac{1}{p^2} \sum_{j,k=1}^{p}[(2\beta_S-1) \widehat{\Delta}_{jk}^2 + \{(1- \beta_S) s_{jk} - \beta_I u_{jk}\}^2 ]$$
is an unbiased estimate of the risk \ref{frobenius risk}, where $\widehat{\Delta}_{jk}^2 = \sum_{i=1}^{n}(X_{ij}X_{ik}-s_{jk})^2 / n$ is the sample variance of $s_{jk}$. The optimal estimator in this class can now be chosen by minimizing $\widehat{R}(\beta_S, \beta_I)$ over $\beta_S$ and $\beta_I$. It can be shown that this is equivalent to estimating the vector $(\sigma_{11}, \ldots, \sigma_{pp})^\top$ by shrinking $(s_{11}, \ldots, s_{pp})^\top$ toward the one-dimensional subspace spanned by $(u_{11}, \ldots, u_{pp})^\top$ \citep{biscarri2019thesis, lindley1962discussion}. Proposition \ref{prop:linear} shows that this subspace shrinkage estimator is identical to the \citet{ledoit2004well} estimator \ref{linear model}.
\begin{prop}
  \label{prop:linear}
  Define the estimator $\widehat{\bs{\Sigma}}_V$ such that its $jk$th entry obeys $\widehat{\sigma}_{jk} = \widehat{\beta}_S s_{jk} + \widehat{\beta}_I u_{jk}$, where $(\widehat{\beta}_S, \widehat{\beta}_I) = \argmin_{\beta_S, \beta_I} \widehat{R}(\beta_S, \beta_I)$. Then $\widehat{\bs{\Sigma}}_V$ = $\widehat{\bs{\Sigma}}_{LW}$.
\end{prop}

@@

The previous section argues that treating covariance matrix estimation as a vector estimation problem can be a fruitful strategy, but discusses only estimators linear in $s_{jk}$. We propose to consider a larger class, the class of so-called separable rules. In the standard compound decision problem of estimating $\bs{\theta}$ using $\bs{Y}$, a separable decision rule $\bs{\delta}(\bs{Y})$ is one where $\delta_i(\bs{Y}) = t(Y_i)$ \citep{robbins1951asymptotically}. Here we generalize this to the problem of estimating a vectorized matrix. For decision rules $\bs{\delta}(\bs{X}) = (\delta_{11}(\bs{X}),\ldots,\delta_{pp}(\bs{X}))$ that estimate $(\sigma_{11}, \ldots, \sigma_{pp})^\top$, define the class of separable rules
\begin{equation}
  \label{separable}
  \mathcal{S} = \{\bs{\delta} : \delta_{jk} = t(\bs{X}_{\cdot j}, \bs{X}_{\cdot k}), j\neq k,\quad 
   \delta_{jj} = \widetilde{t}(\bs{X}_{\cdot j}),j=1,\ldots,p)\},
\end{equation}
where $\bs{X}_{\cdot j} = (X_{1j}, \ldots, X_{nj})^\top$ is the vector of observed values of the $j$th feature. In other words, rules in $\mathcal{S}$ estimate the $jk$th entry of the covariance matrix using a fixed function $t$ of only observations from features $j$ and $k$. The sufficient statistics of $(\bs{X}_{\cdot j}, \bs{X}_{\cdot k})$ is $2\times 2$ matrix
$\begin{bmatrix}
s_{jj} & s_{jk} \\
s_{kj} & s_{kk} 
\end{bmatrix}$.

We propose to search for the optimal estimator within $\mathcal{S}$. This is sensible because $\mathcal{S}$ includes the sample covariance $(s_{11}, \ldots, s_{pp})^\top$, the class of linear estimators \ref{linear class} used by \citet{ledoit2004well}, which can be expressed as
\[
\delta_{jk}(\bs{X}) = \beta_S \bs{X}_{\cdot j}^\top \bs{X}_{\cdot k} / n + \beta_I I(\bs{X}_{\cdot j} = \bs{X}_{\cdot k}),
\]
and the class of adaptive thresholding estimators for sparse covariance matrices studied by \citet{cai2011adaptive}. Therefore the optimal separable estimator $\bs{\delta}^\star$ that minimizes the scaled squared Frobenius risk \ref{frobenius risk} will perform at least as well as these three estimators, and may perform better. Targeting the optimal separable rule is standard in the compound decision literature \citep{zhang2003compound}.

The optimal $\bs{\delta}^\star$ is an oracle estimator and cannot be calculated in practice, as the true risk is unknown. In the classical compound decision framework, empirical Bayes methods are used to estimate the oracle optimal separable rule \citep{robbins1955empirical, zhang2003compound, brown2009nonparametric, jiang2009general, efron2014two, efron2019bayes}. We take a similar approach here. To simplify notation, denote $(\bs{X}_{\cdot j}, \bs{X}_{\cdot k})^\top$ as $\bs{A}_{jk}$. $f(\cdot \mid \bs{\eta}_{jk})$, the density of $\bs{A}_{jk}$, depends on $\bs{\eta}_{jk} = (\sigma_j, \sigma_k, r_{jk})^\top$, where $\sigma_j$ and $\sigma_k$ are the true standard deviations of the $j$th and $k$th covariates and $r_{jk} = \sigma_{jk} / (\sigma_j \sigma_k)$ is their true correlation. When $r_{jk} \ne 1$, $\bs{A}_{jk}$ is comprised of $n$ independent mean-zero multivariate normals with covariance matrices
\[
\bs{C}_{jk}=\begin{bmatrix}
&\sigma_j^2 & \sigma_j\sigma_k r_{jk} \\
& \sigma_j\sigma_k r_{jk}  & \sigma_k^2
\end{bmatrix}.
\]
When $r_{jk} = 1$, $\bs{A}_{jk}$ consists of mean-zero univariate normals with variances $\sigma_j^2$.

Now consider the Bayesian model for non-diagonal entries
\begin{equation}
  \label{bayesian nondiagonal}
  \bs{A} \mid \bs{\eta} \sim f(\cdot \mid \bs{\eta}),
  \quad
  \bs{\eta} \sim G_{nd}(a,b, \gamma) =  \frac{2}{p(p-1)} \sum_{1\leq k<j\leq p} I(\sigma_j \leq a, \sigma_k \leq b, r_{jk} \leq \gamma).
\end{equation}
and diagonal entries
\begin{equation}
  \label{bayesian diagonal}
  \bs{A} \mid a \sim \widetilde{f}(\cdot \mid a),
  \quad
  a \sim G_d(a) =  \frac{1}{p} \sum_{j=1}^p I(\sigma_j \leq a).
\end{equation}
By the fundamental theorem of compound decisions \citep{robbins1951asymptotically, jiang2009general}, this is closely related to the vectorized covariance matrix estimation problem under Frobenius risk \ref{frobenius risk}: for any separable $\bs{\delta} \in \mathcal{S}$ \ref{separable}, the Frobenius risk can be written as
\begin{align*}
  R(\bs{\Sigma}, \bs{\delta})
  =\,&
  \frac{1}{p^2} \{\sum_{1\leq k<j\leq p}^p
  \int \{t(\bs{A}) - \sigma_{jk} \}^2 f(\bs{A} \mid \bs{\eta}_{jk}) d\bs{A} 
  +
  \sum_{j=1}^p
  \int \{\widetilde{t}(\bs{X}) - \sigma_{jj} \}^2 \widetilde{f}(\bs{X} \mid s_{jj}) d\bs{X}
  \}\\
  =\,&
  \frac{p-1}{p}\int \int \{t(\bs{A}) - g(\bs{\eta})\}^2 f(\bs{A} \mid \bs{\eta}) dG_{nd}(\bs{\eta}) d\bs{A}
  +
  \frac{1}{p}\int \int \{\widetilde{t}(\bs{X}) - a^2\}^2 \widetilde{f}(\bs{X} \mid a) dG_{d}(a) d\bs{X} \\
  =\,&
   \frac{p-1}{p}\bb{E}[\{t(\bs{A}) -  g(\bs{\eta})\}^2]+ \frac{1}{p}\bb{E}[\{\widetilde{t}(\bs{X}) -  a^2\}^2],
\end{align*}
where $g(a, b, \gamma) = a b \gamma$ and the final expectation is the Bayes risk of estimating $\sigma_{jk}$. The optimal oracle separable rule $\bs{\delta}^\star$ therefore has $jk$th entry equal to $\delta^\star_{jk}(\bs{X}) = t^\star(\bs{A}_{jk})$ for $j\neq k$ and $\delta^\star_{jj}(\bs{X}) = \widetilde{t}^\star(\bs{X}_{\cdot j})$, where $t^\star = \mathbb{E}\{g(\bs{\eta}) \mid \bs{A}\}$ and $\widetilde{t}^\star = \mathbb{E}\{g(a) \mid \bs{X}\}$ minimizes the Bayes risk.

Based on this result, we propose the following empirical Bayes procedure. We first use nonparametric maximum likelihood \citep{kiefer1956consistency} to estimate the prior $G_p$. Under the Bayesian model \ref{bayesian}, and the working assumption that the $\bs{A}_{jk}$ are independent across $jk$, we estimate $G_{nd}$ using
\begin{equation}
  \label{Gnd hat}
  \widehat{G}_{nd} = \argmax_{G \in \mathcal{G}_{nd}} \prod_{1\leq k<j<p} \int f(\bs{A}_{jk} \mid \bs{\eta}) dG(\bs{\eta}),
\end{equation}

estimate $G_d$ using
\begin{equation}
  \label{Gd hat}
  \widehat{G}_d = \argmax_{G \in \mathcal{G}_d} \prod_{j = 1}^p \int \widetilde{f}(\bs{X} \mid a) dG(a),
\end{equation}
where $\mathcal{G}_{nd}$ is the family of all distributions supported on $\mathbb{R}_+ \times \mathbb{R}_+ \times [-1, 1]$,   $\mathcal{G}_{d}$ is the family of all distributions supported on $\mathbb{R}$. Of course, the $\bs{A}_{jk}$ are not independent, so $\widehat{G}_p$ does not maximize a likelihood but rather a pairwise composite likelihood \citep{varin2011overview}. Using $\widehat{G}_p$, we estimate the vectorized $\bs{\Sigma}$ using $ \widehat{\bs{\delta}}(\bs{X})
  =
  (\widehat{t}(\bs{A}_{21}), \ldots,  \widehat{t}(\bs{A}_{p,p-1}),\widehat{t}(\bs{X}_{\cdot 1}),\ldots,\widehat{t}(\bs{X}_{\cdot p}))$, where 
\begin{equation}
  \label{proposed}
  \widehat{t}(\bs{A}_{jk}) = \frac{\int g(\bs{\eta}) f(\bs{A}_{jk} \mid \bs{\eta})d\widehat{G}_{nd}(\bs{\eta})}{\int f(\bs{A}_{jk} \mid \bs{\eta}) d\widehat{G}_{nd}(\bs{\eta})},
  \quad 
  \widehat{t}(\bs{X}_{\cdot j}) = \frac{\int a^2 \widetilde{f}(\bs{X}_{\cdot j} \mid a)d\widehat{G}_d(a)}{\int \widetilde{f}(\bs{X}_{\cdot j} \mid a) d\widehat{G}_d(a)}.
\end{equation}
The $\widehat{t}$ estimates the Bayes rule $t^\star$ and $\widehat{\bs{\delta}}$ estimate the optimal oracle separable rule $\bs{\delta}^\star$.

>>>>

Covariance matrix estimation is a fundamental statistical problem that plays an essential role in various applications, such as portfolio management \citep{ledoit2003improved}, genomics \citep{schafer2005shrinkage}, and array signal processing \citep{abramovich2001locally}. However, in modern problems the number of features can be of the same order as or exceed the sample size, and the standard sample covariance matrix estimator behaves poorly in this regime. To overcome these issues, various methods have been developed to estimate high-dimensional covariance matrces. These can roughly be divided into two groups, according to whether they impose assumptions of the structure of population covariance matrix.

Structured methods make structural assumptions about the population covariance matrix. One class models the population covariance matrix as sparse. The most common method to address this problem is thresholding \citep{rothman2009generalized, cai2011adaptive}. Penalized likelihood methods \citep{xue2012positive} can also estimate large-scale sparse covariance matrix by penalizing a log-likelihood function. Another class of methods assume the data arise from a factor model \citep{fan2008high}, so that the covariance matrix has low intrinsic dimension. Other common structured methods assume that the covariance matrix is banded \citep{li2017estimation} or Toeplitz matrix \citep{liu2017covariance}.

In contrast, unstructured methods do not make any assumptions about the population covariance matrix, yet still have less estimation error comparing to the sample covariance matrix. A first example was the linear shrinkage approach of \citet{ledoit2004well}, which shrinks the sample covariance matrix toward a scaled identity matrix. More recently, nonlinear shrinkage methods were developed \citep{ledoit2012nonlinear, ledoit2019quadratic, lam2016nonparametric}. These shrink the eigenvalues of the sample covariance matrix toward clusters. Linear shrinkage can be viewed as a special case of nonlinear shrinkage, as it shrinks sample eigenvalues toward their global mean.

Nonlinear shrinkage estimators have desirable optimality properties \citep{ledoit2018analytical} and show excellent performance. However, as the class of rotation-equivariant estimators \citep{stein1975estimation, stein1986lectures}, nonlinear shrinkage estimators modify only the sample eigenvalues and keep the sample eigenvectors. It is known that sample eigenvectors are not consistent estimators of population eigenvectors when the dimension and the sample size increase at the same rate \citep{mestre2008asymptotic}. This suggests that there may exist a class of unstructured estimators that can outperform nonlinear shrinkage.

@@

Here we propose a new unstructured estimator for high-dimensional covariance matrices. Our approach centers on vectorizing the covariance matrix and treating matrix estimation as a vector estimation problem. We do this because it allows us to use a nonparametric empirical Bayes shrinkage procedure, which has been shown in the compound decision literature to have excellent properties \citep{jiang2009general, koenker2014convex}. We then reassemble the estimated vector into matrix form and project onto the space of positive-definite matrices to give our final estimator. Surprisingly, though our vectorized approach essentially ignores the matrix structure, it can still substantially outperform a number of state-of-the-art proposals in simulations and a real data analysis. Our approach is similar to \citet{dey2018corshrink}, which also applied empirical Bayes shrinkage method to estimate correlation matrix. Different from our method, their corShrink method has different target and they do not shrink standard deviations.

The article is organized as follows. In Section \eqref{sec:method}, we briefly review compound decision theory and then introduce our proposed approach. In Section \eqref{numerical results} we illustrate the performance of our method in simulations and a gene expression dataset. Finally, Section \eqref{sec:discussion} concludes with a discussion. Our procedure is implemented in the R package \verb|cole|, available on GitHub.

@@

Our proposed approach is motivated by two observations. First, \eqref{frobenius risk} shows that estimating $\bs{\Sigma}$ under Frobenius risk is equivalent to simultaneously estimating every component of the vector $(\sigma_{11},\ldots,\sigma_{pp})^\top$ under a loss function that aggregates errors across components. Second, this type of vector estimation problem has been well-studied in the compound decision literature. Thus, recent advances in vector estimation may be profitably applied to covariance matrices.

We first briefly review compound decision problems. Introduced by \citet{robbins1951asymptotically}, these problems study the simultaneous estimation of multiple parameters $\bs{\theta} = (\theta_1, \ldots, \theta_n)^\top$ given data $\bs{Y} = (Y_1, \ldots, Y_n)^\top$, with $Y_i\sim P_{\theta_i}$. Specifically, the goal is to develop a decision rule $\bs{\delta}(\bs{Y}) = (\delta_1(\bs{Y}),\ldots,\delta_n(\bs{Y}))$ that minimizes the compound risk
\begin{equation}
\label{compound risk}
R(\bs{\theta},\bs{\delta}) = \frac{1}{n}\sum_{i=1}^n \bb{E} L(\theta_i,\delta_i(\bs{Y}))
\end{equation}
where $L$ is a loss function measuring the accuracy of $\delta_i(\bs{Y})$ as an estimate of $\theta_i$. A classical example is the homoscedastic Gaussian sequence problem, where $Y_i \sim N(\theta_i, 1)$ independently and $L(t, d) = (t - d)^2$ is the squared error loss \citep{johnstone2017gaussian}.

@@

We propose to apply some of these recent vector estimation ideas to covariance matrix estimation. Clearly, covariance matrix estimation under the Frobenius risk \eqref{frobenius risk} can be viewed as a compound decision problem. Furthermore, some existing covariance matrix estimation procedures can already be interpreted as taking a vector approach. The sample covariance matrix $\bs{S}=\frac{1}{n}\bs{X}^{T}\bs{X}$, for instance, can be thought of as estimating each component of $(\sigma_{11},\ldots,\sigma_{pp})^\top$ using maximum likelihood. Less trivially, \citet{cai2011adaptive} studied sparse high-dimensional covariance matrices and explicitly appealed to the vector perspective. Their adaptive thresholding method is a version of the soft thresholding method of \citet{donoho1995adapting}, which was originally developed to estimate a sparse mean vector in the Gaussian sequence problem.

Interestingly, we can also show that the celebrated linear shrinkage covariance matrix estimator of \citet{ledoit2004well} can be interpreted as a vector estimator. The estimator is defined as
\begin{equation}
\label{linear model}
\widehat{\bs{\Sigma}}_{\text{LW}} = \widehat{\rho}_{\text{LW}} \bs{S} + (1-\widehat{\rho}_{\text{LW}})\widehat{\mu} \bs{I}
\end{equation} 
where $\widehat{\mu} = \text{tr}(\bs{S})/p$, and $\widehat{\rho}_{\text{LW}} = 1 - b_n^2 / d_n^2$ for $d_n^2=\|\bs{S}-\widehat{\mu} \bs{I} \|_F^2$ and $b_n^2 = \sum_{i=1}^n \| \bs{X}_i \bs{X}_i^\top - \bs{S} \|_F^2 / n^2$. Now consider the problem of estimating the vectorized $\bs{\Sigma}$ under risk \eqref{frobenius risk}. We restrict attention to decision rules that estimate each component $\sigma_{jk}$ using
\begin{equation}
  \label{linear class}
  \beta_S s_{jk} + \beta_I u_{jk},
\end{equation}
where $s_{jk}$ is the $jk$th entry of $\bs{S}$, $u_{jk}$ is the $jk$th entry of $\bs{I}$, and the class is indexed by the parameters $(\beta_S, \beta_I)$. As proved in appendix, we can show that
$$URE(\beta_S,\beta_I) = \frac{1}{p^2} \sum_{j,k=1}^{p}[(2\beta_S-1) \widehat{\Delta}_{jk}^2 + \{(1- \beta_S) s_{jk} - \beta_I u_{jk}\}^2 ]$$
is an unbiased estimator of the risk \eqref{frobenius risk}, where $\widehat{\Delta}_{jk}^2 = \sum_{i=1}^{n}(X_{ij}X_{ik}-s_{jk})^2 / n(n-1)$ is an unbiased estimator of variance of $s_{jk}$. The optimal estimator in this class can now be chosen by minimizing $URE(\beta_S, \beta_I)$ over $\beta_S$ and $\beta_I$. It can be shown that this is equivalent to estimating the vector $(\sigma_{11}, \ldots, \sigma_{pp})^\top$ by shrinking $(s_{11}, \ldots, s_{pp})^\top$ toward the one-dimensional subspace spanned by $(u_{11}, \ldots, u_{pp})^\top$ \citep{biscarri2019thesis, lindley1962discussion}. Proposition \eqref{prop:linear} shows that this subspace shrinkage estimator is identical to the \citet{ledoit2004well} estimator \eqref{linear model}.
\begin{prop}
  \label{prop:linear}
  Define the estimator $\widehat{\bs{\Sigma}}_V$ such that its $jk$th entry obeys $\widehat{\sigma}_{jk} = \widehat{\beta}_S s_{jk} + \widehat{\beta}_I u_{jk}$, where $(\widehat{\beta}_S, \widehat{\beta}_I) = \argmin_{\beta_S, \beta_I} \widehat{R}(\beta_S, \beta_I)$. Then the coefficients $\widehat{\beta}_S$, $\widehat{\beta}_I $ and $\widehat{\rho}_{\text{LW}}$, $(1-\widehat{\rho}_{\text{LW}})\widehat{\mu}$ are very closed.

  \end{prop}

@@

The previous section argues that treating covariance matrix estimation as a vector estimation problem can be a fruitful strategy, but discusses only estimators linear in $s_{jk}$. We propose to consider a larger class, the class of so-called separable rules. In the standard compound decision problem of estimating $\bs{\theta}$ using $\bs{Y}$, a separable decision rule $\bs{\delta}(\bs{Y})$ is one where $\delta_i(\bs{Y}) = t(Y_i)$ \citep{robbins1951asymptotically}. Here we generalize this to the problem of estimating a vectorized matrix. For decision rules $\bs{\delta}(\bs{X}) = (\delta_{11}(\bs{X}),\ldots,\delta_{pp}(\bs{X}))$ that estimate $(\sigma_{11}, \ldots, \sigma_{pp})^\top$, define the class of separable rules
\begin{equation}
  \label{separable}
  \mathcal{S} = \{\bs{\delta} : \delta_{kj} = \delta_{jk} = t(\bs{X}_{\cdot j}, \bs{X}_{\cdot k}),\, 1\leq k<j\leq p,\quad 
   \delta_{jj} = \widetilde{t}(\bs{X}_{\cdot j}),\,j=1,\ldots,p)\},
\end{equation}
where $\bs{X}_{\cdot j} = (X_{1j}, \ldots, X_{nj})^\top$ is the vector of observed values of the $j$th feature. In other words, rules in $\mathcal{S}$ estimate the $jk$th entry of the covariance matrix using a fixed function $t$ of only observations from features $j$ and $k$. The sufficient statistics of $(\bs{X}_{\cdot j}, \bs{X}_{\cdot k})$ is $2\times 2$ matrix of $S$ denoted by $\bs{S}_{jk}=
\begin{bmatrix}
s_{jj} & s_{jk} \\
s_{kj} & s_{kk} 
\end{bmatrix}$.

We propose to search for the optimal estimator within $\mathcal{S}$. This is sensible because $\mathcal{S}$ includes the sample covariance $(s_{11}, \ldots, s_{pp})^\top$, the class of linear estimators \eqref{linear class} used by \citet{ledoit2004well}, which can be expressed as
\begin{align*}
\delta_{jk}(\bs{X})&= \delta_{kj}(\bs{X})= \beta_S \bs{X}_{\cdot j}^\top \bs{X}_{\cdot k} / n, \, 1\leq k<j\leq p\\
\delta_{jj}(\bs{X})&=\beta_S \bs{X}_{\cdot j}^\top \bs{X}_{\cdot j} / n+\beta_I, \, j=1,\ldots,p
\end{align*}
and the class of adaptive thresholding estimators for sparse covariance matrices studied by \citet{cai2011adaptive}. Therefore the optimal separable estimator $\bs{\delta}^\star$ that minimizes the scaled squared Frobenius risk \eqref{frobenius risk} will perform at least as well as these three estimators, and may perform better. Targeting the optimal separable rule is standard in the compound decision literature \citep{zhang2003compound}.

The optimal $\bs{\delta}^\star$ is an oracle estimator and cannot be calculated in practice, as the true risk is unknown. In the classical compound decision framework, empirical Bayes methods are used to estimate the oracle optimal separable rule \citep{robbins1955empirical, zhang2003compound, brown2009nonparametric, jiang2009general, efron2014two, efron2019bayes}. We take a similar approach here. $f(\cdot \mid \bs{\eta}_{jk})$, the density of $(\bs{X}_{\cdot j}, \bs{X}_{\cdot k})$, depends on $\bs{\eta}_{jk} = (\sigma_j, \sigma_k, r_{jk})^\top$, where $\sigma_j$ and $\sigma_k$ are the true standard deviations of the $j$th and $k$th covariates and $r_{jk} = \sigma_{jk} / (\sigma_j \sigma_k)$ is their true correlation. When $j\neq k$, $(\bs{X}_{\cdot j}, \bs{X}_{\cdot k})$ is comprised of $n$ independent mean-zero multivariate normals with covariance matrices
\[
\bs{C}_{jk}=\begin{bmatrix}
&\sigma_j^2 & \sigma_j\sigma_k r_{jk} \\
& \sigma_j\sigma_k r_{jk}  & \sigma_k^2
\end{bmatrix}.
\]

Now consider the Bayesian model for non-diagonal entries
\begin{equation}
  \label{bayesian nondiagonal}
  (\bs{X},\bs{X}^{'}) \mid \bs{\eta} \sim f(\cdot \mid \bs{\eta}),
  \quad
  \bs{\eta} \sim G_{nd}(a,b, \gamma) =  \frac{2}{p(p-1)} \sum_{1\leq k<j\leq p} I(\sigma_j \leq a, \sigma_k \leq b, r_{jk} \leq \gamma).
\end{equation}
and diagonal entries
\begin{equation}
  \label{bayesian diagonal}
  \bs{X} \mid a \sim \widetilde{f}(\cdot \mid a),
  \quad
  a \sim G_d(a) =  \frac{1}{p} \sum_{j=1}^p I(\sigma_j \leq a).
\end{equation}
the $G_d$ is the marginal density for the first parameter of $G_{nd}$
\begin{equation}
\label{eq:marginal}
\int dG_{nd}(a,b,\gamma)dbd\gamma = dG_d(a)
\end{equation}
By the fundamental theorem of compound decisions \citep{robbins1951asymptotically, jiang2009general}, this is closely related to the vectorized covariance matrix estimation problem under Frobenius risk \eqref{frobenius risk}. Then we have the following proposition.

\begin{prop}\label{prop:bayes risk}
For any $\bs{\delta} \in \mathcal{S}$ \eqref{separable}, the Frobenius risk can be written as the convex combination of Bayesian risks with respect to priors $G_{nd}$ and $G_d$.
\begin{align*}
  R(\bs{\Sigma}, \bs{\delta})
  =\,&
  \frac{1}{p^2} \{2\sum_{1\leq k<j\leq p}^p
  \int \{t(\bs{X},\bs{X}^{\prime}) - \sigma_{jk} \}^2 f(t(\bs{X},\bs{X}^{\prime}) \mid \bs{\eta}_{jk}) d\bs{X}d\bs{X}^{\prime}\\
  +\,&
  \sum_{j=1}^p
  \int \{\widetilde{t}(\bs{X}) - \sigma_{jj} \}^2 \widetilde{f}(\bs{X} \mid s_{jj}) d\bs{X}
  \}\\
  =\,&
  \frac{p-1}{p}\int \int \{t(\bs{X},\bs{X}^{\prime}) - g(\bs{\eta})\}^2 f((\bs{X},\bs{X}^{\prime})\mid \bs{\eta}) dG_{nd}(\bs{\eta}) d\bs{X}d\bs{X}^{\prime}\\
  +\,&
  \frac{1}{p}\int \int \{\widetilde{t}(\bs{X}) - a^2\}^2 \widetilde{f}(\bs{X} \mid a) dG_{d}(a) d\bs{X} \\
  =\,&
   \frac{p-1}{p}\bb{E}[\{t(\bs{X},\bs{X}^{\prime}) -  g(\bs{\eta})\}^2]+ \frac{1}{p}\bb{E}[\{\widetilde{t}(\bs{X}) -  a^2\}^2],
\end{align*}
where $g(a, b, \gamma) = a b \gamma$ and the final expectation is the Bayes risk of estimating $\sigma_{jk}$. 
\end{prop}
The decision rule which minimizes the Frobenius risk depends on all the $\sigma_j$ and $r_{jk}$. The optimal oracle separable rule $\bs{\delta}^\star$ therefore has $jk$th entry equal to $\delta^\star_{jk}(\bs{X}) = t^\star((\bs{X}_{\cdot j},\bs{X}_{\cdot k}))$ for $j> k$ and $\delta^\star_{jj}(\bs{X}) = \widetilde{t}^\star(\bs{X}_{\cdot j})$, where $t^\star = \mathbb{E}\{g(\bs{\eta}) \mid (\bs{X},\bs{X}^{'})\}$ and $\widetilde{t}^\star = \mathbb{E}\{a^2 \mid \bs{X}\}$ minimizes the Bayes risk.
